---
title: "ryx"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{ryx}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ryx)
```

# Introduction

This is a package to compute correlations from a data frame. It also creates
a  custom type called 'ryx' when calling the ryx function, and
custom functions for printing, summarizing and plotting these objects are 
in this package.

#  ryx
Computes the correlations, and stores it in a 'ryx' object that has
the dependent, independent, and a data frame stored within that contains more
use info

```{r}
library(MASS)
x <- ryx(Boston, y="medv")

#or an example using the independent variable parameter
data(mtcars)
x <- ryx(mtcars, y="mpg", x=c("wt", "vs"))

```

# print.ryx
Takes an ryx object and prints a correlation dataframe displaying
correlation and significance for each variable.

```{r}
print(ryx(Boston, y="medv"))
print(ryx(mtcars, y="mpg", x=c("wt", "vs")))
```

# summary.ryx
Provides some summary statistics about the correlations, such as:
median correlation, range of correlation, how many variables were
statistically significant.

```{r}
summary(ryx(Boston, y="medv"))
summary(ryx(mtcars, y="mpg", x=c("wt", "vs")))
```

# plot.ryx
Plots a ryx object as a scatter plot where the x axis is correlation and y-axis are independent
variables

```{r}
plot(ryx(Boston, y="medv"))
plot(ryx(mtcars, y="mpg", x=c("wt", "vs")))
```

